Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
A bunch of edits throughout.  I think this may finish it.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@113 36274a68-8941-4c93-80ef-affaed5139da

\include{jessePreamble} % contains commonly used packages/defined functions
\date{}
\author{Jesse Chan and Nathan V. Roberts}
\title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}

@@

The concept of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time. However, this idea proved to be impractical, as the cost of computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh. The key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space. For a Discontinuous Galerkin method, the test space is also necessarily discontinuous, which decouples the global problem into a local problem over each element.

With respect to optimal test functions, a discontinuous test space allows the test functions to be computed \emph{locally}, on an per-element basis. Not only does this decrease the problem size dramatically, it is also intrinsically parallel---the optimal test functions for each element can be computed completely independently of each other.

@@

In DG methods, elements are coupled to each other through a numerical flux defined on the boundary; for standard DG methods, this numerical flux is computed using some predetermined function of the finite element solution in the interior. The DPG method is an example of a hybridized DG formulation, where the numerical flux is instead solved for as part of the solution, introducing additional unknowns to the problem (called hybridization).

However, this hybridization produces more loosely coupled blocks in the global stiffness matrix than standard DG methods, which, for certain numerical fluxes, will produce the same coupled sparsity pattern as a CG method. For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom. The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, implying that, for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced. Thus, we expect the assembly process to scale to large numbers of processors fairly well.

@@

Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution---the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.  Trilinos's Intrepid routines are designed to execute on batches of cells that are alike in topology and polynomial order.  We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.  Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging for elements of a given ElementType.

@@

To facilitate experiments with multiple partitioning strategies (and to maintain separation of concerns), we designed an abstract MeshPartitionPolicy class which, given a Mesh and the number of partitions desired, returns a partition of the elements in the mesh.  The Mesh then uses this to generate a partition of the degree-of-freedom coefficients, which induces a partition of the rows in the stiffness matrix.  The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix assembly facility within Trilinos.  The FECrsMatrix allows storage of data not owned by the current MPI node; this data is communicated to the owning MPI node during global assembly of the stiffness matrix.  A convenient consequence of this is that we can separate the cost of global assembly from the cost of local stiffness matrix computations; the latter are independent across MPI nodes, and therefore we expect to see perfect scaling for these.  The scaling of the global assembly will depend on the quality of the partition and the cost of communication between MPI nodes.  We do not hope for perfect scaling here, but we do hope to see a cost per degree of freedom per node that does not grow too quickly in the total number of nodes.

The MeshPartitionPolicy partitions the mesh into sets of elements assigned to an MPI node; for the interface to Epetra, we need a partition of rows of the global stiffness matrix (each of which corresponds to a degree of freedom).  Degrees of freedom corresponding to numerical fluxes are shared by the elements along whose boundaries they lie.  We adopt a simple greedy policy for this---shared d.o.f.s are assigned to the element with the smallest global identifier.  This means that even if the element partitioning were perfectly balanced, some MPI nodes might still have more d.o.f.s assigned to them than others.  This will not affect the amount of work involved in local stiffness matrix computations, but it may affect MPI communication costs during global assembly.

@@

Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after KLU has scattered according to the original partitioning.  We hope to eliminate this dependence on having all solution coefficients available, allowing the solution to be distributed according to the same mapping as was used for the stiffness matrix.

@@

The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2 or 3 dimensional space, then mapping that curve to the interval $[0,1]$. The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and maps each of those partitions back into 2 or 3D. All that's required of the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element. In this case, we use the element centroid as such an identifier.

The Reftree algorithm \cite{REFTREE} adds complexity in that each processor must store information not only about the active nodes, but the ancestors as well. Additionally, Reftree requires that, if you store an ancestor, you must store all its children as well, increasing the amount of redundancy between distributed refinement trees. However, due to Reftree being more agnostic towards element types (quad vs triangle, tetrahedron vs cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).  Additionally, Reftree's algorithm guarantees connected partitions for tetrahedral and triangular grids, and generally performs more robustly on other types of grids as well.

Currently, Reftree has been implemented and tested on local clusters. However, Reftree currently crashes during runs on our HPC architecture for this report. We use the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

@@

We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.  We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the north and east edges of the square.

\begin{figure}[h!]
\centering
\includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
\caption{Computed solution for $\epsilon=10^{-2}$ using a refined mesh.  $L^2$ error is $O(10^{-5})$.}
\end{figure}

@@

We also used contiguous and discontiguous partitions of each mesh to measure the effect of partition quality on the communication costs in global stiffness matrix assembly.  We created contiguous partitions of the mesh using a HSFC partitioner.  To create the discontiguous partitioning, we chose to use the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.  After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.  We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here represents its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.

@@

\begin{figure}[h!]
\centering
\subfigure[Cyclic partitioning]{
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC partitioning]{
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\caption{Contiguous and discontiguous partitions of the mesh.}
\end{figure}

@@

It is less clear what we should expect for the global stiffness matrix assembly; we expect the HSFC partitioning to outperform the cyclic partitioning, and we would like to see the runtimes for assembly decrease as the number of MPI nodes increases.  As can be seen in Figures \ref{fig:strongScalingAssemblyCyclic} and \ref{fig:strongScalingAssemblyHSFC}, for the larger problems in both cases, we do have something approaching strong scalability.  For the 202- and 808-element problems, we see the time cost increase (or fail to decrease, in the case of the 808-element problem for the cyclic partitioner) between 16 and 64 nodes.  However, it's worth noting that in these cases, the real times involved are small: less than a second in each case.  If our concern is our ability to scale up to large problems on large numbers of processors, it does not appear that the global assembly will be a bottleneck.  The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioner took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partition.

@@

Both partition types achieve weak scalability in the local stiffness matrix computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.  In fact, we see the total runtime \emph{decrease} slightly as the total workload and number of MPI nodes increase---we are unsure of the reason for this. Similarly, although we would expect the partitioning not to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.

Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}. It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still only a small fraction of the time spent on computation of local stiffness matrices.

\subsection{Breakdown of time spent}

\begin{figure}[h!]
\centering
\subfigure[202 elements, 13343 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52137 dofs ]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3232 elements, 206081 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12928 elements, 819393 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
\end{figure}

\section{Future work}\label{sec:FutureWork}

\subsection{$hp$-meshes}

The Zoltan partitioner supports a weighted partitioning of a set of objects.  At the moment, every element is treated with equal weight, under the assumption that each contributes an equal number of degrees of freedom.  We would like to extend the partitioning to $hp$-adaptive meshes (where the polynomial order $p$ is allowed to vary element by element) by weighting each element by the number of internal degrees of freedom that it holds.

\subsection{Parallel solvers}
\subsubsection{MUMPS}

\subsubsection{Conjugate gradients/static condensation}

One benefit of DPG is that the global stiffness matrices it produces are guaranteed to be symmetric positive-definite, allowing for iterative methods like CG to be used.

Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom. Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield 
\[
\left(\begin{array}{cc}
A &B\\
B^T &C
\end{array}
\right)
\left(\begin{array}{c}
u\\
f
\end{array}
\right) = 
\left(\begin{array}{c}
F\\
G
\end{array}
\right)
\]
where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
\[
(C-B^TA^{-1}B)f = G-B^TA^{-1}F
\]
Since $A$ is easy to invert, and $B$ is a much smaller system, this static condensation would reduce the cost of the solve.

@@

>>>>

\include{jessePreamble} % contains commonly used packages/defined functions
\date{}
\author{Jesse Chan \and Nathan V. Roberts}
\title{Extending Camellia for Distributed Stiffness Matrix Determination in DPG}

@@

The concept of an optimal test function is rigorously defined in \cite{DPG2}, and has been well-known in the finite element community for some time. However, the idea was considered impractical, as the cost of computing a single optimal test function was equivalent to the cost of solving the original problem over the entire mesh. A key contribution of DPG has been to note that the global nature of this problem is due to the continuous nature of the trial space. For a discontinuous Galerkin method, the test space is also necessarily discontinuous, which decouples the global problem into element-local problems.

A discontinuous test space allows the test functions to be computed \emph{locally}, on a per-element basis. Not only does this decrease the problem size dramatically, it is also intrinsically parallel---the optimal test functions for each element can be computed independently of each other.

@@

In DG methods, elements are coupled to each other through a numerical flux defined on the boundary; for standard DG methods, this numerical flux is computed using some predetermined function of the finite element solution in the interior. The DPG method is an example of a hybridized DG formulation, which means that the numerical flux is solved for as part of the solution by introducing additional unknowns to the problem.

Whereas standard DG methods can (for certain numerical fluxes) produce global stiffness matrices whose elements are as tightly coupled as a CG method would, hybridization produces more loosely coupled blocks in the matrix.  For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom. The interior degrees of freedom (of which there are usually many more than boundary degrees of freedom) for each element are decoupled from each other.  Thus the inter-node communication required during global stiffness matrix assembly is reduced. We therefore expect the assembly process to scale to large numbers of processors, particularly if we use a good partitioner.

@@

Camellia was originally written to run in serial, so a number of changes were required to allow MPI execution---the most significant of these had to do with element partitioning and partitioning the degree-of-freedom coefficients.  Trilinos's Intrepid routines are designed to execute on batches of cells that are alike in topology and polynomial order.  We allow meshes of non-uniform topology and polynomial order; thus we had implemented an ElementType class which allowed us to identify elements that could be batched.  Our Mesh class maintained data structures such that information pertaining to a particular ElementType could be accessed quickly---for example, Mesh stored a data structure that contained the vertex coordinates belonging to elements of a given ElementType.

@@

To facilitate experiments with multiple partitioning strategies (and to maintain separation of concerns), we designed an abstract MeshPartitionPolicy class which, given a Mesh and the number of partitions desired, returns a partition of the elements in the mesh.  The Mesh then uses this to generate a partition of the degree-of-freedom coefficients, which induces a partition of the rows in the stiffness matrix.  The latter partition is used in conjunction with an Epetra FECrsMatrix, a distributed stiffness matrix class within Trilinos.  The FECrsMatrix allows storage of data not owned by the current MPI node; this data is communicated to the owning MPI node during global assembly of the stiffness matrix.  A convenient consequence of this is that we can separate the cost of global assembly from the cost of local stiffness matrix computations; the latter are independent across MPI nodes, and therefore we expect to see perfect scaling for these.  The scaling of the global assembly will depend on the quality of the partition and the cost of communication between MPI nodes.  We do not hope for perfect scaling here, but we do hope to see a cost per degree of freedom per node that does not grow too quickly in the total number of nodes.

The MeshPartitionPolicy partitions the mesh into sets of elements assigned to an MPI node; for the interface to Epetra, we need a partition of rows of the global stiffness matrix (each of which corresponds to a degree of freedom).  Degrees of freedom corresponding to numerical fluxes are shared by the elements along whose boundaries they lie.  We adopt a simple greedy policy for assignment of these d.o.f.s: shared d.o.f.s are assigned to the element with the smallest global identifier.  This means that even if the element partitioning were perfectly balanced, some MPI nodes might still have more d.o.f.s assigned to them than others.  This will not affect the amount of work involved in local stiffness matrix computations, but it may affect MPI communication costs during global assembly.

@@

Finally, certain features of the original code depend upon all the solution coefficients being available to the current processor, so for the time being we distribute the entire solution to every MPI node, after Amesos has scattered according to the original partitioning.  We hope to eliminate this dependence on having all solution coefficients available, allowing the solution to be distributed according to the same mapping as was used for the stiffness matrix.

@@

The Hilbert space-filling curve (HSFC) algorithm works by drawing a curve through the geometric mesh in 2- or 3-dimensional space, then mapping that curve to the interval $[0,1]$. The partitioner then divides up this interval (in an even or weighted manner) into $n$ partitions, and uses this partitioning to induce a partition of the mesh. All that's required by the HSFC algorithm is a listing of elements and a geometric identifier associated with a given element. In this case, we use the element centroid as such an identifier.

The Reftree algorithm \cite{REFTREE} adds complexity in that each processor must store information not only about the active nodes, but the ancestors as well. Reftree also requires that if you store an ancestor, you also store all its children as well, increasing the amount of redundancy between distributed refinement trees. However, since Reftree is not tuned to a particular element types (quad or triangle, tetrahedron or cube), the same algorithm performs similarly for many different types of refined meshes (as opposed to HSFC, which works best for quadrilateral grids, but not for triangular grids).  Additionally, Reftree's algorithm guarantees connected partitions for tetrahedral and triangular grids, and generally performs more robustly on other types of grids as well.

Currently, we have implemented and tested a Reftree MeshPartitionPolicy on our workstations. However, Reftree currently crashes during runs on Lonestar, our HPC architecture for this report. We used the HSFC partitioner for the scaling tests in this report, and hope to fix issues with Reftree in the near future.

@@

We tested the scalability of our code on the Lonestar machine at the Texas Advanced Computing Center (TACC), verifying whether or not we observe strong/weak scaling for various parts of the program.  We solve the convection-diffusion equation on a square mesh, with boundary conditions such that the solution develops a boundary layer (sharp gradient) near the north and east edges of the square.  The solution for a refined mesh is shown in Figure \ref{fig:solutionPlot}.

\begin{figure}[h!]
\centering
\includegraphics[scale=\oneFig]{figs/Solution12928nomesh.png}
\caption{Computed solution for $\epsilon=10^{-2}$ using a 12,928-element mesh.  $L^2$ error is $O(10^{-5})$.}
\label{fig:solutionPlot}
\end{figure}

@@

We also used contiguous and discontiguous partitions of each mesh to measure the effect of partition quality on the communication costs in global stiffness matrix assembly.  We created contiguous partitions of the mesh using a HSFC partitioner.  To create the discontiguous partitioning, we used the Zoltan cyclic partitioner, which loops through the list of active elements, sending the first element to the first processor, the next to the next processor, and so on.  After reaching the last processor, the cyclic partitioner cycles back to the first processor and repeats this process.\footnote{Due to the nature of our refinements in this test, a blocked partitioner (equally partitioning the ordered list of active elements by element number) happened to produce nearly-contiguous partitions.  We therefore have omitted this partitioner from our analysis, since we do not believe that its performance here accurately predicts its performance in general.}  The cyclic partitioning is a ``worst case" scenario in the sense that each of the current MPI node's elements' neighbors are owned by some other MPI node, with the consequence that information concerning each element boundary must be sent via MPI.  An example cyclic partitioning can be seen in Figure \ref{fig:cyclicPartition}; Figure \ref{fig:HSFCPartition} shows an HSFC partitioning.

@@

\begin{figure}[h!]
\centering
\subfigure[Cyclic partitioning]{\label{fig:cyclicPartition}
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC partitioning]{\label{fig:HSFCPartition}
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\caption{Discontiguous and contiguous partitions of the mesh.}
\end{figure}

@@

It is less clear what we should expect for the global stiffness matrix assembly; we expect the HSFC partitioning to outperform the cyclic partitioning, and we would like to see the runtimes for assembly decrease as the number of MPI nodes increases.  As can be seen in Figures \ref{fig:strongScalingAssemblyCyclic} and \ref{fig:strongScalingAssemblyHSFC}, for the larger problems in both cases, we do have something approaching strong scalability.  For the 202- and 808-element problems, we see the time cost increase (or fail to decrease, in the case of the 808-element problem for the cyclic partitioner) between 16 and 64 nodes.  However, it's worth noting that in these cases, the real times involved are small: less than a second in each case.  If our concern is our ability to scale up to large problems on large numbers of processors, it does not appear that the global assembly will be a bottleneck.  The HSFC partitioning does show its strength here compared with the cyclic; for the 12,928 mesh on the 4-node run, the cyclic partitioning took an average of 49.1 seconds per node, compared with 1.63 seconds for the HSFC partitioning.

@@

Both partition types achieve weak scalability in the local stiffness matrix computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.  In fact, we see the total runtime \emph{decrease} slightly as the total workload and number of MPI nodes increase---we are unsure of the reason for this. Although we would not expect the partitioning to affect this portion of the computation at all (since no inter-node communication occurs at this stage), for some reason the HSFC partitioning slightly outperforms the cyclic on each of the multi-node runs.  As with the strong scaling, we speculate that this is due to locality of the owned element data in the case of the HSFC partitioning.

Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}. It's worth noting, however, that though the poor mesh partitioning imposes much higher communication costs than the HSFC partitioning, the maximum amount of time spent on assembly is still dominated by the time spent on computation of local stiffness matrices.

\subsection{Total runtime analysis}\label{sec:runtimeAnalysis}
As the final component of our performance analysis, we examine components of the total runtime for each of our four problems using 1, 4, 16, and 64 MPI nodes; here we use the HSFC partitioner.  This can be seen in Figure \ref{fig:timeBreakdown}.  We see that for the largest MPI runs the combined time spent on local stiffness computation and global assembly is a small fraction of the total time spent---since these were the targets of the present work, we can count it a success.  The graphs also show that the cost of the global solve dominates in each of these runs, making this the obvious next target for optimization.  In the ``Other'' category, the largest cost is the mesh determination.  In the 12,928-element case, this takes about 5 seconds.  Thus, a distributed mesh might be our next target after the solve is optimized.

\begin{figure}[h!]
\centering
\subfigure[202 elements, 13,343 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52,137 dofs ]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3,232 elements, 206,081 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12,928 elements, 819,393 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
\label{fig:timeBreakdown}
\end{figure}

\section{Future work}\label{sec:FutureWork}
There are several ways in which we hope to extend Camellia further to allow it to solve larger problems still; we hope to:
\begin{itemize}
\item distribute the solve, using MUMPS or an iterative solver,
\item improve the load balancing for meshes of variable polynomial order,
\item distribute mesh construction and storage, and
\item distribute solution storage.
\end{itemize}

As discussed in Section \ref{sec:runtimeAnalysis} above, the lowest-hanging fruit for further improving the performance for the experimental setup considered in the present work is distributing the solve.  We have already successfully interfaced with MUMPS---a parallel sparse direct solver---on one of our laptops; we expect that getting MUMPS to work on Lonestar will just be a matter of building Trilinos and Camellia with MUMPS there.  One of the advantages of DPG is that its stiffness matrices are guaranteed to be symmetric positive definite, which opens the door to using iterative methods such as conjugate gradient methods.  DPG also produces matrices whose entries are coupled only through the flux degrees of freedom; thus static condensation techniques can be used to reduce the size of the global system to be solved.  (See Appendix \ref{app:staticCondensation} for a brief explanation of what's involved in static condensation.)  We believe that iterative solvers and static condensation would allow us to solve larger problems than MUMPS will allow---we have heard that MUMPS only scales to about 128 processors.

In the present work, we considered a mesh of uniform polynomial order and considered all elements to be of equal weight; Camellia supports meshes with variable order, and Zoltan provides facilities for weighting elements differently.  By taking advantage of this feature of Zoltan (using a weight corresponding to the number of degrees of freedom on each element), we can improve Camellia's load balancing for meshes of variable polynomial order.  In fact, in doing so, we expect to improve slightly the load balancing for the setup considered here, because elements with hanging nodes do have slightly more degrees of freedom than those without.

At present, the mesh is constructed and stored on each node, as is the solution.  It should be a relatively small extension to the present work to allow the solution to be distributed.  Allowing mesh construction to be distributed is a bigger challenge, largely because the nodes must agree on the global stiffness matrix row indices.  Given that we are working with an adaptive mesh, it will likely make sense to distribute the work of mesh refinement according to the partition of the previous mesh and use Zoltan to do the load rebalancing.

In summary, we have achieved good overall speedup for Camellia using a Hilbert space-filling curve partitioner, and have identified the next steps for improving its parallel performance further.

@@

\newpage
\appendix
\section{Static Condensation}\label{app:staticCondensation}

One benefit of DPG's hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom. Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield 
\[
\left(\begin{array}{cc}
A &B\\
B^T &C
\end{array}
\right)
\left(\begin{array}{c}
u\\
f
\end{array}
\right) = 
\left(\begin{array}{c}
F\\
G
\end{array}
\right)
\]
where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
\[
(C-B^TA^{-1}B)f = G-B^TA^{-1}F
\]
Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.
